Recent demography drives changes in linked selection across the maize genome

### 2015-11-16 manuscript.tex
submitted version.

\significancetext{
Both selection and demographic change play important roles in shaping genetic diversity, but there are few empirical examples of the interplay between these forces. We document the combined effects of demography and linked selection on maize genome-wide diversity. After going through a bottleneck ≈5\% of the size of the ancestral teosinte population, recent expansion resulted in a maize population much larger than teosinte. Positive selection on new genic mutations has affected genetic diversity little, but selection against deleterious mutations dramatically reduced diversity within and surrounding genes. The impact of selection depends on the age of the polymorphisms evaluated, revealing that a complete understanding of genome-wide diversity requires careful assessment of demographic history and the effects of linked selection.
} %JRI

@@

\begin{acknowledgments}
We are indebted to Graham Coop and Simon Aeshbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.
\end{acknowledgments}

>>>>

\significancetext{
Both selection and demographic change play important roles in shaping genetic diversity, but there are few empirical examples of the interplay between them. Although it is well known that both diversity and the efficacy of natural selection are reduced in smaller populations, the short-term consequences of demographic change on linked selection have not been well studied. We use wild and domesticated maize to demonstrate that rapid changes in population size impact the effect of selection on linked sites in ways not well described by long-term average population size. We also produce an unbiased estimate of maize demographic history and show that positive selection on new genic mutations plays a lesser role in shaping diversity than purifying selection against deleterious mutations.
} %JRI

@@

\begin{acknowledgments}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.
\end{acknowledgments}
